Estimation and Implications of Bias in EPA Pollution Measurement

### 2021-12-28 paper/5min-presentation/5min-presentation.Rmd
Updated prediction model to include i subscript (so each set of gamma weights is specific to the i'th monitor)
removing some redundancy of filenames.

ggsave('monitor_map_2015-2021.png', width = 6, height = 4)

@@

```{r Map and images, echo=F, warning=F, message=F, fig.width=12, fig.cap='test'}
p_pa = "../../docs/purpleair/PA_outdoor_monitor_border.png"
p_epa = "../../docs/epa/air-monitoring-site_border.jpg"
p_map = 'monitor_map_2015-2021.png'
library(png)
library(jpeg)
library(grid)
library(gridExtra)
img_map = rasterGrob(as.raster(readPNG(p_map)), interpolate = FALSE)
img1 <-  rasterGrob(as.raster(readPNG(p_pa)), interpolate = FALSE)
img2 <-  rasterGrob(as.raster(readJPEG(p_epa)), interpolate = FALSE)

@@

\[
\alert<2>{EPA_{i,t}} = \gamma_{i,0} + \sum\limits_{j\in J_i}\sum\limits_{k=1}^7\gamma_{j,k} 
\alert<3>{PA_{j,t}} \cdot \alert<4>{Winddir_{i,t,k}} + u_{i,t}
\]

\begin{itemize}
\item<1-> Analysis done at the month and quarter level; suppressing that subscript.
\item<1-> $t$ is a unique hour within a given month or quarter.
\item<1-> EPA monitor $i$ at time $t$ reads PM2.5 pollution \alert<2>{$EPA_{i,t}$}.
\item<1-> For each EPA monitor $i$, there are $J_i$ Purple Air monitors within a 10-mile radius.
\item<1-> Purple Air monitor $j\in J_i$ at time $t$ reads PM2.5 pollution \alert<3>{$PA_{j,t}$}.
\item<1-> $\alert<4>{Winddir_{i,t,k}} $ is a wind direction indicator; 1 if the prevailing wind near station $i$ at time $t$ is in the $k^{th}$ bucket (of 8 buckets).
\end{itemize}

>>>>

p_map = 'monitor_map_2015-2021.png'
ggsave(map_filename, width = 6, height = 4)

@@

```{r Map and images, echo=F, warning=F, message=F, fig.width=12, fig.cap='test'}
p_pa = "../../docs/purpleair/PA_outdoor_monitor_border.png"
p_epa = "../../docs/epa/air-monitoring-site_border.jpg"
library(png)
library(jpeg)
library(grid)
library(gridExtra)
img_map = rasterGrob(as.raster(readPNG(map_filename)), interpolate = FALSE)
img1 <-  rasterGrob(as.raster(readPNG(p_pa)), interpolate = FALSE)
img2 <-  rasterGrob(as.raster(readJPEG(p_epa)), interpolate = FALSE)

@@

\[
\alert<2>{EPA_{i,t}} = \gamma_{i,0} + \sum\limits_{j\in J_i}\sum\limits_{k=1}^7\gamma_{i,j,k} 
\alert<3>{PA_{j,t}} \cdot \alert<4>{Winddir_{i,t,k}} + u_{i,t}
\]

\begin{itemize}
\item<1-> Each EPA monitor $i$ has it's own set of weights for the PA sensors around it.
\item<1-> Analysis done at the month and quarter level; suppressing quarter subscript.
\item<1-> $t$ is a unique hour within a given month or quarter.
\item<1-> EPA monitor $i$ at time $t$ reads PM2.5 pollution \alert<2>{$EPA_{i,t}$}.
\item<1-> For each EPA monitor $i$, there are $J_i$ Purple Air monitors within a 10-mile radius.
\item<1-> Purple Air monitor $j\in J_i$ at time $t$ reads PM2.5 pollution \alert<3>{$PA_{j,t}$}.
\item<1-> $\alert<4>{Winddir_{i,t,k}} $ is a wind direction indicator; 1 if the prevailing wind near station $i$ at time $t$ is in the $k^{th}$ bucket (of 8 buckets).
\end{itemize}
